### 2016-09-30 architecture.tex
The design isn't just simplified by interning
Add another reference to the supplement

Another important property of SymPy expressions is that they are immutable.
This simplifies the design of SymPy by allowing expression interning. It also
enables expressions to be hashed, which allows expressions to be used as keys
in Python dictionaries, and is used to implement caching in SymPy.

@@

The typical way to create a custom SymPy object is to subclass an existing
SymPy class, usually \texttt{Basic}, \texttt{Expr}, or \texttt{Function}. As
it was stated before, all SymPy classes used for expression trees should be
subclasses of the base class \texttt{Basic}. \texttt{Expr} is the
\texttt{Basic} subclass for mathematical objects that can be added and
multiplied together. The most commonly seen classes in SymPy are subclasses of
\texttt{Expr}, including \texttt{Add}, \texttt{Mul}, and \texttt{Symbol}.
Instances of \texttt{Expr} typically represent complex numbers, but may also
include other ``rings'', like matrix expressions. Not all SymPy classes are
subclasses of \texttt{Expr}. For instance, logic expressions, such as
\verb|And(x, y)|, are subclasses of \texttt{Basic} but not of \texttt{Expr}.

>>>>

Another important property of SymPy expressions is that they are immutable.
This simplifies the design of SymPy, and enables expression interning. It also
enables expressions to be hashed, which allows expressions to be used as keys
in Python dictionaries, and is used to implement caching in SymPy.

@@

The typical way to create a custom SymPy object is to subclass an existing
SymPy class, usually \texttt{Basic}, \texttt{Expr}, or \texttt{Function}. As
it was stated before, all SymPy classes used for expression trees should be
subclasses of the base class \texttt{Basic}. \texttt{Expr} is the
\texttt{Basic} subclass for mathematical objects that can be added and
multiplied together. The most commonly seen classes in SymPy are subclasses of
\texttt{Expr}, including \texttt{Add}, \texttt{Mul}, and \texttt{Symbol}.
Instances of \texttt{Expr} typically represent complex numbers, but may also
include other ``rings'', like matrix expressions. Not all SymPy classes are
subclasses of \texttt{Expr}. For instance, logic expressions, such as
\verb|And(x, y)|, are subclasses of \texttt{Basic} but not of
\texttt{Expr}.\footnote{See the supplement for more information on the
  \texttt{sympy.logic} submodule.}
